Insights on the Impact of Context in the Perception of a Robot

### 2015-06-15 main.tex
Fixed rendering of citations by switching to Lualatex

\documentclass[lettersize, apacite, twoside, HRI]{apa_HRI}

\usepackage[utf8x]{inputenc}

\usepackage{times}

\usepackage{graphicx} 
\usepackage{subfigure}
\usepackage{paralist}
\usepackage{hyperref}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{url}
\usepackage{xspace}
\usepackage{booktabs}

@@

\author{Séverin Lemaignan, Ashish Ranjan Jha, Kshitij Sharma, Pierre
Dillenbourg}
\affiliation{CHILI Lab, École Polytechnique Fédérale de Lausanne}

@@

\bibliography{biblio}

>>>>

\documentclass[lettersize, noapacite, twoside, HRI]{apa_HRI}

%\usepackage[utf8x]{inputenc}
\usepackage{times}

\usepackage{graphicx} 
\usepackage{subfigure}
\usepackage{paralist}

\usepackage{hyperref}

\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{url}
\usepackage{xspace}
\usepackage{booktabs}

\usepackage[natbibapa]{apacite}

@@

\author{S\'everin Lemaignan, Ashish Ranjan Jha, Kshitij Sharma, Pierre
Dillenbourg}
\affiliation{CHILI Lab, \'Ecole Polytechnique F\'ed\'erale de Lausanne}

@@

\bibliographystyle{apacite}
\bibliography{biblio}
